Optimal Task Phasing for End-To-End Latency in Harmonic Systems and Semi-Harmonic Automotive Systems

### 2024-10-01 paper.tex
automotive max-harmonic

%% PAPER SPECIFIC:
\usetikzlibrary{patterns}
\ifCLASSOPTIONcompsoc
	\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
	\usepackage[caption=false,font=footnotesize]{subfig}
\fi

@@

@@

	\begin{theorem}[Optimality]
		If $\Tbb_E$ is max-harmonic, then the task phasing presented in Equation~\eqref{eq:phasing} minimizes the end-to-end latency.
		In particular, the suggested phasing minimizes the end-to-end latency in harmonic systems.
	\end{theorem}

@@

	Look at task set with automotive periods 1,2,5,10,20,50,100,200,1000

>>>>

%% PAPER SPECIFIC:
\usetikzlibrary{patterns}
\ifCLASSOPTIONcompsoc
	\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
	\usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{enumitem}

@@

\newcommand{\Tmaxone}{T^E_{\mathit{max},1}}
\newcommand{\Tmaxtwo}{T^E_{\mathit{max},2}}

@@

	\begin{theorem}[Optimality]\label{thm:optimal_max_harmonic}
		If $\Tbb_E$ is max-harmonic, then the task phasing presented in Equation~\eqref{eq:phasing} minimizes the end-to-end latency.
		In particular, the suggested phasing minimizes the end-to-end latency in harmonic systems.
	\end{theorem}

@@

	In industrial applications, systems are not always fully harmonic. 
	Rather, systems are \emph{almost} harmonic (also called semi-harmonic).
	Especially in the automotive domain, it is common that task periods are chosen such that 
	\begin{equation}
		T_\tau \in T^{\mathit{Aut}} := \setof{1,2,5,10,20,50,100,200,1000} 
	\end{equation} 
	for all $\tau \in \Tbb$,
	as specified by real-world automotive benchmarks~\cite{kramer2015real}.
	In this section, we discuss how our findings from Section~\ref{sec:harmonic} can be extended to such semi-harmonic automotive systems.
	That is, we consider the cause-effect chain $E = (\tau_1 \to\dots\to \tau_n)$ with $T_{\tau_i} \in T^{\mathit{Aut}}$ for all $i=1, \dots, n$.
	For notational convenience, we denote by 
	\begin{equation}
		\Tmaxone := \max \set{T_{\tau_i}}{\tau_i\in \Tbb_E}
	\end{equation}
	the maximal period of tasks of $E$, and by 
	\begin{equation}
		\Tmaxtwo := \max \set{T_{\tau_i}}{\tau_i\in \Tbb_E, T_{\tau_i} \neq \Tmaxone}
	\end{equation}
	the second highest period if there is any.
	Otherwise, we let $\Tmaxtwo := 0$ if there are only tasks with one period in $\Tbb_E$.

	First, for cases in which $\Tbb_E$ is max-harmonic we can directly apply the results from Section~\ref{sec:harmonic}.

	\begin{theorem}[Max-Harmonic Automotive]
		If any of the following three cases holds, then the taskset $\Tbb_E$ is max-harmonic and our results from the previous section are applicable:
		\begin{enumerate}[label=(\roman*)]
			\item $\Tmaxone \notin \setof{5,50}$
			\item $\Tmaxone = 5$ and $\Tmaxtwo \neq 2$
			\item $\Tmaxone = 50$ and $\Tmaxtwo \neq 20$
		\end{enumerate}
		In particular, the phasing from Definition~\ref{def:phasing_max_harm} is optimal due to Theorem~\ref{thm:optimal_max_harmonic}, and the end-to-end latency under the phasing from Definition~\ref{def:phasing_max_harm} is given by Theorem~\ref{thm:e2e_with_phasing_harm}.
	\end{theorem}

	\begin{proof}
		Under any of the cases (i), (ii) and (iii), we have
		$\frac{\Tmaxone}{T_{\tau_i}} \in \Nbb$ for all $\tau_i \in \Tbb_E$.
		Therefore, $\Tbb_E$ is max-harmonic, and Theorems~\ref{thm:optimal_max_harmonic} and~\ref{thm:e2e_with_phasing_harm} can be applied.
	\end{proof}
